18 month progress report

### 2017-03-16 reports/progress_1/progress_1.tex
In progress report, added references.

\section{Introduction}
3D printing, or additive layer manufacturing, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.  Recently it has been commercialised and has served purposes in the medical field and engineering. The need for detecting defects from 3D printing is required in order to do quality control, especially if the 3D printed object is used for something critical for example body parts.

X-ray computed tomography (CT) scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles. These x-ray images then can be combined to form a 3D projection and the detection of defects can start. However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation from the x-ray tube to the detector, sources of error or noise is introduced. In order to do defect detection in a statistical manner, sources of error must be considered.

@@

\section{Shading Correction}
The x-ray detector is made up 32 panels, arranged in 2 rows and 16 columns. Unfortunately these panels do obviously show up in the b/g/w images which consequently create panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}. The effects can be described as introducing a gradient to the grey values within panels and perhaps between panels and globally. The aim of shading correction is to remove these effects to estimate the image of the scan if it were to have none of these effects.

Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image. Similarly let $U(x,y)$ be they grey value of pixels of the shading-free image. The shading effects can be modelled using a linear relationship
\begin{equation}
N(x,y) = U(x,y)b(x,y) + a(x,y)
\end{equation} 
where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{young2000shading}. If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
\begin{equation}
\widehat{U}(x,y) = \frac{N(x,y)-\widehat{a}(x,y)}{\widehat{b}(x,y)} \times c_1 + c_2
\end{equation}
where $c_1$ and $c_2$ are some constants.
One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the mean black and white (b/w) images. Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean black and white images respectively, then the estimators for $b(x,y)$ and $a(x,y)$ are
\begin{equation}
\widehat{b}(x,y) = \overline{W}(x,y) - \overline{B}(x,y)
\end{equation}
and
\begin{equation}
\widehat{a}(x,y) = \overline{B}(x,y)
\end{equation}
respectively.

@@

To avoid dealing with dead pixels, a method was considered which smoothed the reference images prior to any shading correction parameter estimation. The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically. Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}. The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}. A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit. In the black and grey images, the residuals show a global ring which is very unusual for the black image because it is detecting no x-rays at all. The b/g/w residuals all show vertical stripes. The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects. Higher order polynomials can be considered but overfitting may be possible, as a result of higher order polynomials attempting to capture all the characteristics of the b/g/w images.

@@

>>>>

\section{Introduction}
3D printing, or additive layer manufacturing \cite{kodama1981automatic} \cite{wong2012review}, can be used to create objects with complicated shapes and geometry from a blueprint, or CAM model, on a computer.  Recently it has been commercialised and has served purposes in the medical field \cite{kang20163d} and engineering \cite{wong2012review}. The need for detecting defects from 3D printing is required in order to do quality control, especially if the 3D printed object is used for something critical for example body parts.

X-ray computed tomography (CT) \cite{hounsfield1980computed} \cite{michael2001x} \cite{cantatore2011introduction} scans can be used to take images of a rotating 3D printed sample to obtain images of the sample at multiple angles. These x-ray images then can be combined to form a 3D projection and the detection of defects can start. However due to the random nature of x-ray photons in its production in an x-ray tube and attenuation from the x-ray tube to the detector, sources of error or noise is introduced. In order to do defect detection in a statistical manner, sources of error must be considered.

@@

\section{Shading Correction}
The x-ray detector was made up 32 panels, arranged in 2 rows and 16 columns. Unfortunately these panels can be observed in the b/g/w images as a result of panel-wise effects in the image of the sample, as shown in Figure \ref{fig:image}. The effects can be described as introducing a gradient to the grey values within panels and perhaps between panels and globally. The aim of shading correction is to remove these effects to estimate the image of the scan if it were to have none of these effects.

Let $N(x,y)$ be the grey value of the pixel at position $(x,y)$ in the obtained image. Similarly let $U(x,y)$ be they grey value of pixels of the shading-free image. The shading effects can be modelled using a linear relationship
\begin{equation}
N(x,y) = U(x,y)b(x,y) + a(x,y)
\end{equation} 
where $b(x,y)$ is the multiplicative effect and $a(x,y)$ is the additive effect \cite{munzenmayer2003enhancing}. If it is possible to estimate the functions $b(x,y)$ and $a(x,y)$ using the estimators $\widehat{b}(x,y)$ and $\widehat{a}(x,y)$ respectively, then the shading-free image can be estimated using the estimator
\begin{equation}
\widehat{U}(x,y) = \frac{N(x,y)-\widehat{a}(x,y)}{\widehat{b}(x,y)} \times c_1 + c_2
\end{equation}
where $c_1$ and $c_2$ are some constants.
One method to estimate the images $b(x,y)$ and $a(x,y)$ is to use the mean black and white (b/w) images. Let $\overline{B}(x,y)$ and $\overline{W}(x,y)$ be the sample mean black and white images respectively, then the estimators for $b(x,y)$ and $a(x,y)$ are
\begin{equation}
\widehat{b}(x,y) = \overline{W}(x,y) - \overline{B}(x,y)
\end{equation}
and
\begin{equation}
\widehat{a}(x,y) = \overline{B}(x,y)
\end{equation}
respectively \cite{young2000shading}.

@@

To avoid dealing with dead pixels \cite{brettschneider2014spatial}, a method was considered which smoothed the reference images prior to any shading correction parameter estimation. The purpose of this was to iron out any misbehaving pixels in the reference images and to capture the shading effects parametrically. Second order panel-wise surface polynomials were fitted to the b/g/w images, this is shown in Figure \ref{fig:polynomial_shadingCorrection}. The standardised residuals from the panel-wise fit are shown in Figure \ref{fig:polynomial_residual}. A quick inspection of the residuals shows any characteristics not captured by the panel-wise fit. In the black and grey images, the residuals show a global ring which is very unusual for the black image because it is detecting no x-rays at all. The b/g/w residuals all show vertical stripes. The panel-wise fit can be improved by including a global polynomial fit to capture between panel effects. Higher order polynomials can be considered but overfitting may be possible, as a result of higher order polynomials attempting to capture all the characteristics of the b/g/w images.

@@

Additional methods for shading correction could be considered such as fitting a global polynomial in addition to the panel wise polynomials to the reference images. There exist methods which do not require reference images at all, such as entropy minimisation \cite{likar2000retrospective}, which could be studied further and may be useful here.
